Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2016-12-31 paper/ms.tex
Dirac -> Kronecker
Added ACF figure for SHO section.

To scale GP models to larger datasets, \citet{Rybicki:1995} presented a method
of computing \eq{gp-likelihood} in $\mathcal{O}(N)$ when the covariance
function is
\begin{eqnarray}
k_\bvec{\alpha}(\tau_{nm}) = \sigma_n^2\,\delta_{nm} + a\,\exp(-c\,\tau_{nm})
\end{eqnarray}
where $\{{\sigma_n}^2\}_{n=1}^N$ are the measurement uncertainties,
$\delta_{nm}$ is the Dirac delta, and $\bvec{\alpha} = (a,\,c)$.
The intuition behind this method is that, for the choice of $k_\bvec{\alpha}$,
the inverse of $K_\bvec{\alpha}$ is tridiagonal and can it can be computed
with a small number of operations for each data point.
Subsequently, \citet{Ambikasaran:2015} generalized this method to arbitrary
mixtures of exponentials
\begin{eqnarray}
k_\bvec{\alpha}(\tau_{nm}) = \sigma_n^2\,\delta_{nm} +
    \sum_{j=1}^J a_j\,\exp(-c_j\,\tau_{nm})\quad.
\end{eqnarray}
In this case, the inverse will be dense but \eq{gp-likelihood} can still be
evaluated in $\mathcal{O}(J^2\,N)$ operations where $J$ is the number of
components in the mixture and $N$ is still the number of data points.

@@

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=0.75\textwidth]{figures/sho.pdf}
\caption{The power spectrum of a stochastically-driven simple harmonic
    oscillator (\eqalt{sho-psd}) plotted for several values of the quality
    factor $Q$.
    For comparison, the dashed line shows the Lorentzian function from
    \eq{lorentz-psd} with $c_j = 2\,Q = 20$ and normalized so that
    $S(d_j) = Q^2 = 100$.
    \figurelabel{sho}}
\end{center}
\end{figure}

>>>>

To scale GP models to larger datasets, \citet{Rybicki:1995} presented a method
of computing \eq{gp-likelihood} in $\mathcal{O}(N)$ when the covariance
function is
\begin{eqnarray}
k_\bvec{\alpha}(\tau_{nm}) = \sigma_n^2\,\delta_{nm} + a\,\exp(-c\,\tau_{nm})
\end{eqnarray}
where $\{{\sigma_n}^2\}_{n=1}^N$ are the measurement uncertainties,
$\delta_{nm}$ is the Kronecker delta, and $\bvec{\alpha} = (a,\,c)$.
The intuition behind this method is that, for the choice of $k_\bvec{\alpha}$,
the inverse of $K_\bvec{\alpha}$ is tridiagonal and can it can be computed
with a small number of operations for each data point.
Subsequently, \citet{Ambikasaran:2015} generalized this method to arbitrary
mixtures of exponentials
\begin{eqnarray}
k_\bvec{\alpha}(\tau_{nm}) = \sigma_n^2\,\delta_{nm} +
    \sum_{j=1}^J a_j\,\exp(-c_j\,\tau_{nm})\quad.
\end{eqnarray}
In this case, the inverse will be dense but \eq{gp-likelihood} can still be
evaluated in $\mathcal{O}(J^2\,N)$ operations where $J$ is the number of
components in the mixture and $N$ is still the number of data points.

@@

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/sho.pdf}
\includegraphics[width=0.5\textwidth]{figures/acf_sho.pdf}
\caption{(top) The power spectrum of a stochastically-driven simple harmonic
    oscillator (\eqalt{sho-psd}) plotted for several values of the quality
    factor $Q$.
    For comparison, the dashed line shows the Lorentzian function from
    \eq{lorentz-psd} with $c_j = 2\,Q = 20$ and normalized so that
    $S(d_j) = Q^2 = 100$. (bottom) The corresponding autocorrelation functions.
    \figurelabel{sho}}
\end{center}
\end{figure}
